\section{Conclusions and Future Work}\label{Sec:concl}
To control the severe spreading\cite{spreading} of COVID-19 and reduce the heavy labor cost in this pandemic, disinfection plays an important role. A new type of disinfection robot is designed. It provides a solution for precise fixed-point and full coverage alcohol spraying disinfection.

The designed robot is a combination of a mobile base and robot arm with an alcohol sprayer as an end-effector. Three-Mecanum-Wheel Configurations is the mobile base to make the robot suitable for working in a medical environment. As for the robot arm, the structure is identical to that of RB-1. Regarding its motion, SLAM is applied for localization and mapping, and algorithms like Morse Decompositions and ClearGrasp are inserted for solving various situations of a robot such as avoiding unexpected obstacles and recognizing transparent objects.

In the future, methods for disinfection can be explored further，such as ultralviolet used in UVD robots.\cite{FLEMING2018241} End-effector which is an alcohol sprayer currently, should able to be replaced by other devices such as ultralviolet light, realizing disinfection with higher efficiency.
With the development of modern society, the human-robot interaction is a focus and can be explored further under well-designed research the medical robotics.\cite{medicalkansei} According to the concept of Kansei engineering\cite{kansei}, some elements of our robot perhaps can be replaced by other structures or material under the circumstance of maintaining the original function. 