\section{Hypothesis and Evaluation}\label{Sec:evaluation}

\par In order to detect the accuracy of precise point and complete full coverage of alcohol spray and disinfection, the coverage rate is introduced as the evaluation index of robot disinfection. Fluorescent reagents are used instead of alcohol in the experiment to visualize the coverage. After the experiment is over, detect the objects to be disinfected and the fluorescent reagents in the experimental scene to evaluate the accuracy of the disinfection. The experiment will be carried out as follows.
\par The experiment will be divided into two parts, the first part detects precise point disinfection, and the second part detects complete coverage of disinfection. First, create an experimental scene, a confined space about 40 square meters in size, including two rooms A and B. Place an experiment table in the two rooms, and place an object to be disinfected on the two experiment tables, for example, an ornament. At the same time, obstacles are placed in each room to detect the obstacle avoidance function of the robot. After starting the robot, the robot will enter rooms A and B in turn to carry out disinfection work. The scope of disinfection includes the entire house and objects to be disinfected. After the robot returns to its original position after the disinfection work is completed, the coverage rate of the fluorescent reagent in the room and the coverage rate of the fluorescent reagent on the surface of objects are detected to evaluate the accuracy of detecting precise points and complete coverage of alcohol spray and disinfection, respectively.



